Macro Impacts

### 2016-07-21 Macro Impacts Revised.tex
Test for the final time
General Source
Something that Prof. Starkman anticipated from the beginning.

@@

\pagebreak
\section{Numerical Methods}
From symmetry, it is clear that it is enough to understand the behavior of rays from a point source to understand the propagation of rays in the whole sphere. Let $\vec p=(r,\theta)$ denote the position vector of our ray, whose initial coordinates are $\vec p(0)=(z,0)$.

\pagebreak
\section{Melt Zone}
As derived in ''A time dependent model for long-rod penetration" the plastic zone (i.e. the melt zone) around an impacting projectile is given by $\alpha*R$, where $\alpha$ is given by 
\begin{align}
(1+\frac{\rho_t u^2}{Y_t})\sqrt{K_t - \rho_t \alpha^2 u^2} = (1+\frac{\rho_t \alpha^2 u^2}{2G_t})\sqrt{K_t - \rho_t u^2}.
\end{align}
where $u$ is the velocity of the projectile (i.e. the macro), $\rho_t$, $K_t$, $G_t$ and $Y_t$ are the density, bulk modulus, sheer modulus, and flow stress of the target (i.e. earth or the moon) respectively.

>>>>

\section{A General Pressure Wave}
We now do the same calculation assuming that the pressure wave is of finite height, cylindrically symmetric, and of finite radial support. Moreover, we assume that the radial pressure distribution can be written as a taylor series. Write
p=p_0f(r)\ps{\theta\p{z+\f h2}-\theta\p{z-\f h2}}
We may expand $f$ as
f(r)&=\sum_{n=0}^\infty\f{f^{(n)}(r_0)}{n!}(r-r_0)^n\,,\\
&=\sum_{n=0}^\infty\sum_{m=0}^n(-1)^{n-m}\binom{n}{m}\f{f^{(n)}(r_0)}{n!}r^{m}r_0^{n-m}\,.
We now Fourier transform
P(\vec k)=\f{4\pi p_0}{k_z}\sin\p{\f{h k_z}{2}}\sum_{n=0}^\infty\sum_{m=0}^n\f{f^{(n)}(r_0)}{n!}\f{(-r_0)^{n-m}}{2+m}\ps{x^{2+m}\,_q\te{F}_p\p{\pc{1+\f m2},\pc{1,2+\f m2},-\f14 x^2 k_r^2}}_{x=a}^b\,,
where $_q\te{F}_p$ is the generalized hypergeometric function. We now convert to spherical coordinates in $k$-space, and write
P(\vec k)=\f{4\pi p_0}{k\cos\theta}\sin\p{\f{h k\cos\theta}{2}}\sum_{n=0}^\infty\sum_{m=0}^n\f{f^{(n)}(r_0)}{n!}\f{(-r_0)^{n-m}}{2+m}\ps{x^{2+m}\,_q\te{F}_p\p{\pc{1+\f m2},\pc{1,2+\f m2},-\f14 x^2 k^2\sin^2\theta}}_{x=a}^b\,,
We now expand the hypergeometric function to first order (the first order term is zero, so all that remains is the zeroth order term)
P(\vec k)&=\f{4\pi p_0}{k\cos\theta}\sin\p{\f{h k\cos\theta}{2}}\sum_{n=0}^\infty\sum_{m=0}^n\f{f^{(n)}(r_0)}{n!}\f{(-r_0)^{n-m}}{2+m}\ps{x^{2+m}}_{x=a}^b+\scr O(k^2)\,,\\
&=\ps{\f{4\pi p_0}{k\cos\theta}\sin\p{\f{h k\cos\theta}{2}}x^2\underbrace{\sum_{n=0}^\infty\sum_{m=0}^n\f{f^{(n)}(r_0)}{n!}\f{(-r_0)^{n-m}}{2+m}x^{m}}_{f_1(x)}}_{x=a}^b+\scr O(k^2)\,,\\
&=\f{4\pi p_0}{k\cos\theta}\sin\p{\f{h k\cos\theta}{2}}(b^2f_1(b)-a^2f_1(a))+\scr O(k^2)\,.
From this, we find that the energy in the lowest modes is
E_{\te{propagated}}&=\f{\lambda+2\mu}{K^2}2p_0^2(b^2f_1(a)-a^2f_1(b))^2\p{-2k_0+k_0\cos(h k_0)+\f{\sin(h k_0)}{h}+h k_0^2\te{Si}(h k_0)}+\scr O(k_0^4)\,,\\
&\approx_{h\gg k_0}\f{\lambda+2\mu}{K^2} \f{4 p_0^2h\pi^3(b^2 f_1(b)-a^2f_1(a))^2}{\lambda_0^2}\,.
Let's do some checks. First consider the basic cylinder pressure where $f=1$ on $[0,r_X]$. Then $f_1=\f12$, and we see that
E&\approx\f{\lambda+2\mu}{K^2}\f{p_0^2h\pi^3r_X^4}{\lambda_0^2}\,,\\
&=\f{\lambda+2\mu}{K^2}(p_0\sigma_X)^2\f{\pi h}{\lambda_0^2}\,,
which is exactly the result from before. Now consider $f(r)=\f{r-r_0}{\Delta r}$ on $[r_0,r_0+\Delta r]$. Then, taking the endpoint $r_0$ as the base of the Taylor series, $f_1(x)=\f{-r_0}{2\Delta r}+\f{x}{3\Delta r}$. Hence
E&\approx\f{\lambda+2\mu}{K^2}\f{h p_0^2\pi^3\Delta r^2(3r_0+2\Delta r)^2}{9\lambda_0^2}
This is what we find out later! I'm legitimately surprised that I didn't make a mistake! Woo!

@@

\pagebreak
\section{Numerical Methods}
From symmetry, it is clear that it is enough to understand the behavior of rays from a point source to understand the propagation of rays in the whole sphere. Let $\vec p=(r,\theta)$ denote the position vector of our ray, whose initial coordinates are $\vec p(0)=(z,0)$. We also insist that the tangent vector of $\vec p$ be at an angle $\alpha$ from the z axis.
\pagebreak
\section{Melt Zone}
As derived in ''A time dependent model for long-rod penetration" the plastic zone (i.e. the melt zone) around an impacting projectile is given by $\alpha*R$, where $\alpha$ is given by 
\begin{align}
(1+\frac{\rho_t u^2}{Y_t})\sqrt{K_t - \rho_t \alpha^2 u^2} = (1+\frac{\rho_t \alpha^2 u^2}{2G_t})\sqrt{K_t - \rho_t u^2}.
\end{align}
where $u$ is the velocity of the projectile (i.e. the macro), $\rho_t$, $K_t$, $G_t$ and $Y_t$ are the density, bulk modulus, sheer modulus, and flow stress of the target (i.e. earth or the moon) respectively.
